Community context determines competition/facilitation trade-offs in pollination systems

### 2019-04-18 paper/manuscript.Rmd
Couple more edits to discussion

How precisely plants balance the costs and benefits in the short and the long term likely depends on the species sensitivity to different risks but also, as we show here, on the community it belongs to. 
<!-- The mechanisms through which sharing pollinators may induce net competition are relatively well understood.  -->
<!-- It can occurr for example, when a more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].  -->
<!-- Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed.  -->
<!-- Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs. outcross-pollen may differ in their value for fertilization (TODO: ref needed).  -->
<!-- However, it is reasonable to expect that the difference between these two may be generally relevant.  -->
<!-- Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).  -->
For instance, a plant species that experience a large reduction in seed set due to heterospecific pollen deposition might be better off by sharing few pollinators, while sharing pollinators makes more sense for those mainly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].
Nevertheless, the observed diversity of the facilitation/competition outcomes across communities and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity. 
Although there are exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised. 
While it is possible, from an evolutionary perspective, that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history, we show that most plant species are still flexible enough to adopt markedly different niches in different communities. 
From a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
Our results highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours. 
This is so because the outcome might depend not only on the particular niche each species occupies in a particular community but also on other factors that we were unable to measure [e.g. pollinator behaviour and densities or spatial context; @ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009].
However, our results also suggest that introduced species are more likely to be beneficial if they have different traits to local plants. 
<!-- cite melissa's paper if available before publication -->

>>>>

The strong contribution of the random effects in our models suggest that the effects of pollen deposition can vary greatly among species. 
For instance, for some plant species even low amounts of heterospecific pollen deposition can have a large impact on fitness while other species might be instead limited by the amount of conspecific pollen deposited by animal pollination [@campbell_mechanism_1985; @arceo-gomez_interactive_2019]. 
Similarly, plant species can also differ on the extent to which self- vs. outcross-pollen differ in their value for fertilization. 
For species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy), even 
Wether some patterns indicate facilitation or competition might

Beyond species identity, however we show that the way plants balance the costs and benefits of sharing pollinators, beyond species identity, is strongly determined by the community it belongs to.

Different species balance the costs and benefits differently as the effects of conspecific and 
Here we also show that  
Na
<!-- The mechanisms through which sharing pollinators may induce net competition are relatively well understood.  -->
<!-- It can occurr for example, when a more dominant species, monopolizes a limited number of pollinators [@mitchell_new_2009; @lopezaraizamikel_impact_2007], when heterospecific pollen deposited in the stigma phisically interferes with deposition of conspecific pollen [@runquist_pollinator-mediated_2012], or when conspecific pollen is lost to heterospecific stigmas [@mitchell_new_2009; @muchhala_interspecific_2012].  -->
<!-- Similarly, not all species had more pollen deposited when open to animal pollination compared to when they were closed.  -->
<!-- Although it can be important, we were unable to test the effect of pollen viability or the extent to which self- vs. outcross-pollen may differ in their value for fertilization (TODO: ref needed).  -->
<!-- However, it is reasonable to expect that the difference between these two may be generally relevant.  -->
<!-- Particularly so for species that are not self-fertile or those in which self-fertilization is rarely effective due to a temporary separation in the maturation of the sexes (dichogamy) (TODO: ref needed).  -->
Nevertheless, the observed diversity of the facilitation/competition outcomes across communities and the relevance of random effects in our models suggests that the community context has a very important effect on the way plant species respond to competition for pollination beyond species identity. 
Although there are exceptions, some plant families (Asteraceae for example) are often generalists in their communities while others (Orchidaceae) are known to be more commonly specialised. 
While it is possible, from an evolutionary perspective, that selection for a particular strategy might say something about the community in which a species has typically inhabited during its evolutionary history, we show that most plant species are still flexible enough to adopt markedly different niches in different communities. 
From a more applied perspective, flowering plants are sometimes introduced to attract pollinators on other nearby plants. 
Our results highlight the difficulties involved in predicting whether the introduced plant species will facilitate or compete with neighbours. 
This is so because the outcome might depend not only on the particular niche each species occupies in a particular community but also on other factors that we were unable to measure [e.g. pollinator behaviour and densities or spatial context; @ye_competition_2014; @flanagan_effects_2011; @cariveau_spatially_2009].
However, our results also suggest that introduced species are more likely to be beneficial if they have different traits to local plants. 
<!-- cite melissa's paper if available before publication -->
